%%%%%%%%%% Compose a Bailey %%%%%%%%%%
\newcommand\baileydesc{}
\newcommand\baileymarkets{}
\newcommand\baileymarketsWide{}
\newcommand\baileyback{}

\newcommand\addChunkOfBailey{%
  \ifcase\value{segNoSpare}\relax\or%
    \appto{\name}{copper}%
    \appto{\baileydesc}{Copper spikes crown the outer wall.  }%
    \appto{\baileymarketsWide}{\baileyArms}%
  \or%
    \ifodd\thefenestraDay
      \appto{\name}{what}%
      \appto{\baileydesc}{The local \gls{doula} did not appreciate the \gls{village}'s original name, so people changed it to `what'.  }%
    \else
      \appto{\name}{kettle}%
      \appto{\baileydesc}{A wattle cottage stands awkwardly far from \baileyname's walls, beyond the farmland, in a sea of \ifnum\thecycle>3 daffodils\else thorns\fi.  }%
    \fi
    \appto{\baileymarkets}{\doulaCottage}%
  \or%
    \appto{\name}{nut}%
    \appto{\baileydesc}{Walnut tree grow around the farmland in a grand circle.
    They say walnuts keep the \gls{edge} at bay.  }%
    \appto{\baileymarkets}{\renewcommand\rations{walnut \ifodd\value{r2}cake\else roast\fi}}%
    \appto{\baileymarketsWide}{}
  \or%
    \appto{\name}{stank}%
    \appto{\baileydesc}{You can smell the local peatbog from a mile away.  }%
    \appto{\baileymarketsWide}{\baileyTanner}%
  \or%
    \appto{\name}{broch}%
    \appto{\baileydesc}{The \gls{village} retains the \gls{broch} which founded the area, though nowadays a retired \gls{ranger} lives there.  }%
    \appto{\baileymarketsWide}{\baileyRanger\par}
  \or%
    \appto{\name}{mill}%
    \appto{\baileydesc}{%
      \ifodd\thediceNo%
        A windmill stands at the side, with an old woman watching your approach from a window.
      \else%
        A small watermill turns gently in the river.
      \fi%
    }%
    \ifnum\value{r12}=9
      \appto{\baileyback}{%
        The mill screams in the darkness.

        \paragraph{Rush through the dark while the miller family remains safe behind their bedroom door,}
        with \roll{Wits}{Athletics} at \tn[9].

        \paragraph{If the creature enters the door,}
        it kills, then retreats with the corpse.
        Chasing it down requires a \roll{Speed}{Athletics} check at \tn[10].

        \ifnum\thetemperature>1
          \chitincrawler
        \else
          \woodspy
        \fi
      }
    \fi
  \or%
    \appto{\name}{trapper}%
    \appto{\baileydesc}{The farmers remind everyone not to `skulk', as the outer fields have bear-traps hidden where you least expect them.  Every farmer here has a good memory.  }%
    \appto{\baileymarketsWide}{\baileyRanger\par}
  \or%
    \appto{\name}{vore}%
    \appto{\baileydesc}{Dogs howl as you approach.  }%
    \appto{\baileymarkets}{\beastSellers}%
    \appto{\baileyback}{\showBeastMarket}%
  \else%
    \appto{\name}{quarry}%
    \appto{\baileydesc}{Half of the settlement is made from stone.  }%
    \appto{\baileymarketsWide}{\baileySmith}%
  \fi%
  \appto{\baileymarkets}{\par}%
}

%%%% The daily bailey  must have text on both sides of the page, so people can
%    orient themselves by it when printing booklets.

\newcommand\afterBaileyEvent{%
  \ifcase\value{goblinLoot}\relax%
  \or% 1
    \appto{\baileyback}{%
      The next evening, people with long, pointed ears arrive from beyond the \gls{edge} to sell.

      \gnollSellers

      \gnollDogShow
    }%
  \or% 2
    \ifnum\thetemperature>1
      \appto{\baileyback}{%
        That night, \pgls{crawler} arrives, climbs over the wall, and feels around the houses for an opening.
        \ifcase\value{r4}\relax\or%
          Distant screams come soon after, as it enters a home.
          \ifodd\value{r2}%
            The rest of the \gls{village} stay inside.
            {\par\sffamily In the morning, remove the last seller.}
          \else%
            Half the \gls{village} come out, with \glspl{torch} and spears to block its escape.
          \fi%
        \or%
          It pads along the roof where the \glspl{pc} sleep, then leaves soon after.
        \else%
          Everyone remains still, and by the morning, it leaves.
        \fi

        \chitincrawler
      }%
    \else%
      \appto{\baileyback}{%
        That night, \pgls{woodspy} arrives, climbs over the wall, and feels around the houses for an opening.
        \ifodd\thefenestraDay
          It leaves soon after, silently, but \baileyname\ remains worried the entire morning.
        \else
          It camouflages into a roof, silently, and waits for the right moment to strike.
        \fi
        \woodspy
      }%
    \fi
  \or% 3
    \appto{\baileyback}{%
      The night passes peacefully.
      Morning arrives with a \showTemperature\ wind.
      A small caravan arrive soon after.
      \composeHumanName\ sells \rations, \rations, and clothes.
      And \composeHumanName\ is happy to buy any \gls{ingredient} for \mkPrice{7}.
    }%
  \or% 4
    \appto{\baileyback}{%
      \begin{boxtext}
        In the dark, two little lights pass quietly between houses; two young people have crept out to meet each other in secret, and everyone in \baileyname\ pretends not to hear them.
      \end{boxtext}
    }%
  \or% 5
    \appto{\baileyback}{%
      The next afternoon, bandits arrive at \baileyname, with \pgls{woodspy} corpse, claiming to be \glspl{guard}.
      This group began as \glspl{fodder} recently, then fled their post, killed their \gls{jotter}, gathered more, and marched a long way here hoping to go unnoticed.
      They still have their black clothing, but know nothing about the local \glspl{guard}.

      If the troupe push their claim, they become irritable, then leave and plan \pgls{ambush} (they don't want the \glspl{pc} telling everyone where they are).

      \humansoldier[\npc{\T[\arabic{r12}]\Hu}{\arabic{noAppearing}~`\Glspl{gDigger}'}]

      \composeHumanName\ speaks for the group, with her
      \ifodd\value{r4b}%
        high-pitched voice%
      \else%
        habit of stamping her feet for immediate attention%
      \fi, and
      \ifodd\value{r4}%
        acne-scarred nose.
      \else%
        weird milky-white eye.
      \fi%

      \ifodd\thefenestraYear
        \humanarcher[\npc{\T[\arabic{r12}]\Hu}{\arabic{noAppearing}~Hiding Bandits}]
      \else
        \humanthief[\npc{\T[\value{r12}]\Hu}{\arabic{noAppearing}~Hiding Bandits}]
      \fi

      \composeHumanName\ does the planning, from the back, while the rest constantly undermine his decisions.
    }%
  \else% 6
    \ifnum\thefenestraDay>50
      \appto{\baileyback}{%
        The next day, everyone in \baileyname\ begins fussing about the impending \gls{storm}.
        They discuss the rooves, possible flooding, and placing buckets of water to prepare for lightning strikes setting something on fire.

        Attempting any further business takes two \glspl{interval} until \gls{storm} subsides.
      }%
    \else
      \appto{\baileyback}{%
        \begin{boxtext}
          Long after Sunset, a trader's voice booms out from beyond the wall.
          He states his prices for ropes and meats, then stops half-way through the sentence.
          Another shouts their prices for clothes.
          The voices repeat their clipped phrases, always identically.
        \end{boxtext}

        If the \glspl{griffin} see one or two people out, they attack.
        Otherwise, they fly away.

        Everyone in \baileyname\ knows that \glspl{griffin} mimic human voices.
        The next day everyone has theories about which trader's voice they heard last night, and what has happened to them now.%
        \ifodd\value{r3b}%
          \footnote{The traders are fine.}%
        \else%
          \footnote{The traders lie dead \arabic{r12} miles up the \glsentrytext{lonelyRoad}.}%
        \fi%

        \griffin[\npc{\T[\value{r2t4}]\A}{\arabic{r2t4}~\Glspl{griffin}}]
      }%
    \fi
    \setcounter{goblinLoot}{0}%
  \fi%
  \addtocounter{goblinLoot}{\value{r2}}%
}

\newcommand\baileyWell{
  \noindent
  \begin{minipage}{\linewidth}
  \begin{speechtext}
    \hspace{3em}\flourish~{\scshape\Large Well}~\flourish
    \par
    \ifodd\value{r12}
      Proper \showTemperature\ today.
    \fi
    \ifnum\thefenestraDay>50
      \Gls{grummel}'s on his way, brewing up some mischief as usual and we're all underprepared.
    \fi
    \ifodd\value{r3}
      \rotatebox{\value{rn1t2}}{Any news from town?}
      \rotatebox{\value{rn1t2}}{\footnotesize Sorry\ldots I forgot yous can't go in\ldots}
    \else
      \rotatebox{\value{rn1t2}}{Remember and buy some rope.}
      \rotatebox{\value{rn1t2}}{If you don' have it, you'll need it.}
    \fi

    \raggedleft
    \ifodd\day
      \footnotesize
      Why don't the \glspl{guard} make weapons?
      Why do they have to buy them from the \glspl{sunGuard}?
    \else
      My son's in the \gls{guard}.
      He kills \pgls{basilisk} a week, but never sends money home.
    \fi
    \normalsize\rm\centering
    \par
    {\sl
    \ifcase\thecycle
      Last week, out with the traders, I heard this little bell from the forest.
      But that's none of my business\ldots
    \or
      \Gls{sable} can go fuck an icicle.
      What kind of god makes snow and just lies in it?
      `Lazy', that's what he is.
    \or
      Warming up, yes, indeed.
      Listen well and you can almost hear the \glspl{basilisk} waking from hibernation.
    \or
      Do you think the water tastes funny?
      Once my ale's done, it'll taste bloody hilarious!
    \or
      \ifodd\thefenestraDay
        Don't bump the watermelons with the bucket, or they'll go bad.
        Come back tonight, and you can have one.
      \else
        I know exactly why \gls{sylf} hates everyone.
        I'm three \glspl{cycle} pregnant, and not up for nothing.
        What do you think of `\composeHumanName' as a name?
      \fi
    \else
      Another year comes to an end.
      Good bloody riddance!
      \thefenestraYear\ was bad for \ifodd\year carrots\else barley\fi, and bad for \ifodd\thefenestraDay wine\else beets\fi.
    \fi
    }
    \ifcase\value{r6}\relax\or%
      {\tiny If I grow up, I want to be \pgls{guard}.}
    \or%
      {\tiny Mum says you have to give me 3~\glsentrylongpl{cp} right now.}
    \or%
      {\tiny Did you ever saw \pgls{crawler} smoking a pipe?}
    \or%
      {\tiny How many \glspl{basilisk} did you killed?}
    \or%
      {\tiny \Pgls{crawler} ate my \ifodd\thefenestraDay grampa \else granny \fi last \gls{cFour}.  Can you kill it for me?}
    \else%
      {\tiny You get to be \pgls{guard} killing people first, then \glspl{monster} my mum said.}
    \fi%
  \end{speechtext}
  \end{minipage}
}

\setcounter{segNoSpare}{\value{r6}}

\newcommand\composeBailey{
  \stepcounter{diceNo}
  \renewcommand\name{}
  \renewcommand\baileydesc{}
  \renewcommand\baileymarkets{}
  \renewcommand\baileymarketsWide{\baileyFletcher\par}
  \renewcommand\baileyback{}
  \ifnum\value{segNoSpare}>6% This counter determines which chunk of bailey-descrption is used.
    \setcounter{segNoSpare}{1}%
  \else%
    \stepcounter{segNoSpare}%
  \fi%
  \addChunkOfBailey
  \addtocounter{segNoSpare}{\value{r3}}
  \addChunkOfBailey

  \appto{\baileymarkets}{%
    \baileyServices\par%
    \baileyHospitality\par%
    \baileySalvage\par%
  }

  % Baileys without a river should have a well.
  \ifodd\thediceNo
    \appto{\baileymarkets}{\baileyWell}
  \else
    \ifodd\value{r4b}
      \appto{\baileydesc}{Men are fixing boats by the shallow river.  One introduces himself as `\marketBoatman'.  }
    \else
      \appto{\baileydesc}{A deep river run through a wicker fence in the wall.  }
    \fi
  \fi

  \appto{\baileymarkets}{%
    \butcherStall\par%
    \baileyWeaver\par%
  }

  \edef\baileyname{\expandafter\MakeUppercase\name}

  \afterBaileyEvent
  \colourWheel[r6]
}

%%%%%%%%%% Bailey Markets %%%%%%%%%%

\newcommand\doulaCottage{
  \noindent
  \begin{minipage}{\linewidth}
    \renewcommand\npcsymbol{\glsentrysymbol{nulla}}
    \begin{nametable}[Lcc]{At \composeHumanName's \Glsentrytext{doulaShop}}
      \textbf{Things on shelves} & \textbf{Weight} & \textbf{Cost} \\\hline
      \rareMarketItem[9]{Air \Glsentrytext{boon}}{1}{24}%
      \rareMarketItem[9]{Fire \Glsentrytext{boon}}{1}{24}%
      \rareMarketItem[8]{Earth \Glsentrytext{boon}}{1}{24}%
      \rareMarketItem[9]{Water \Glsentrytext{boon}}{1}{24}%
      \rareMarketItem[9]{Fate \Glsentrytext{boon}}{1}{24}%
      \marketItem{Cup of tea}{0}{0}%
    \end{nametable}

      \itshape
      \small
      I'll take any \glsentrytext{ingredient} for \arabic{r12}~\glsfmtplural{sp} %
      \ifcase\value{r6b}\relax%
        and \pgls{sp} extra if you can bring my cat `Nothing' back.%
      \else%
        and if yous ever need something in town,
        \footnotesize
        \ifnum\thefootnote>3
          my cousin \composeHumanName\ lives on a nice,
          \scriptsize
          wee patch just outside the gates, so just tell her I sent yous and yous can drop your arms off with her, and pick them back up the moment you leave.
          Best not get in trouble with those \glspl{sunGuard}, eh?
        \else
          say hello to \marketFence\ from his old aunty, okay?
        \fi
      \fi
  \end{minipage}
}

\newcommand\baileyServices{
  \begin{boxtable}[Lc]
    \textbf{Services} & \textbf{Cost} \\\hline
    \composeHumanName, the archer & \mkPrice{1} per mile \\

    \composeHumanName, local guide & \mkPrice[cp]{50} per mile \\
    \ifodd\value{diceNo}\else
      Boat-ride down-river with \marketBoatman%
      \ifodd\value{fenestraDay}%
        \stepcounter{footnote}
        \footnotemark[\thefootnote]
      \fi
      & \mkPrice[cp]{6} per mile \\
      Boat-ride up-river with \composeHumanName\  & \mkPrice[cp]{16} per mile \\
    \fi
  \end{boxtable}
  \ifodd\value{diceNo}\else
    \ifodd\value{fenestraDay}
      \ifnum\thefootnote<3
        \footnotetext{\it Need something in town?  If yous can fit in the barrels, I can drop yous off inside for \pgls{sp} each.}
      \else
        \footnotetext{\it Free for \glspl{guard}.}
      \fi
    \fi
  \fi
}

\newcommand\butcherStall{
  \renewcommand\npcsymbol{\flourish}
  \begin{nametable}[Lc]{At \composeHumanName\ the Butcher's\footnote{\sffamily The butcher buys bodies at half the value of their \gls{cr} in \glspl{sp}, or a quarter if he already has some.}}
    \textbf{Rations} & \textbf{Cost} \\\hline
    \ifnum\value{r12}>8
      Smoked auroch & \mkPrice[cp]{20} \\
    \else
      Boar ears & \mkPrice[cp]{17} \\
    \fi
    \ifodd\thediceNo
      Fresh fish (keeps for a day) & \mkPrice[cp]{6} \\
    \else
      \ifodd\thetrack
        Fishcakes & \mkPrice[cp]{17} \\
      \else
        \ifnum\thetemperature>1
          \Glsfmttext{crawler} pat\'e \& crackers & \mkPrice[cp]{17} \\
        \else
          \Gls{digger} feet & \mkPrice[cp]{9} \\
        \fi
      \fi
    \fi
    \ifnum\value{r12}=8
      Deer jerky  & \mkPrice[cp]{18} \\
    \fi
  \ifnum\thetemperature>2
    Smoked \gls{basilisk} strips & \mkPrice[cp]{4} \\
  \fi
  \end{nametable}
  \vspace{-\baselineskip}
  \begin{speechtext}
    Got anything interesting for the shop?
  \end{speechtext}
}

\newcommand\beastSellers{
  \begin{minipage}{\linewidth}
  \begin{boxtable}[Lc]
    \textbf{Beasts} & \textbf{Cost} \\\hline
    Donkey & \mkPrice{4} \\

    Horse & \mkPrice{20} \\

    Mule & \mkPrice{23} \\

    Hunting Dog & \mkPrice{4} \\

  \end{boxtable}

  {\footnotesize\sffamily \roll{Wits}{Cultivation} to judge the animals at \tn[9].
  If you roll over, turn the page over and look at the animals on the back.
  If you roll a tie, ask the \gls{gm} three questions about the \glsfmtplural{statblock}.}
  \end{minipage}
}

\newcommand\baileyHospitality{
  \begin{boxtable}[Lc]

    \textbf{Hospitality} & \textbf{Cost} \\\hline

    \ifodd\value{r4}
    Bed in \composeHumanName's stable & \mkPrice{0} \\

    Hearty meal with the \composeHumanName\ family and \arabic{r12} kids & \ifnum\value{temperature}=0\mkPrice[cp]{8}\else\mkPrice[cp]{2}\fi \\

    \fi
    Hardened \rations & \mkPrice[cp]{15} \\

    Salty \rations & \mkPrice[cp]{15} \\

  \end{boxtable}
}

\newcommand\baileySalvage{
  \begin{nametable}[Lcc]{\composeHumanName's Wood Salvage Goods}

    \textbf{Travel} & \textbf{Weight} & \textbf{Cost} \\\hline

    \ifodd\value{diceNo}
      Cart & 13 &  \mkPrice{13} \\
      Rushlights & 0 & \mkPrice[cp]{1} \\
    \else
      \setcounter{Strength}{\value{r6}}
      \multiply\value{Strength} by 10
      \addtocounter{Strength}{0}
      Boat for \arabic{r6} & 1\arabic{r6} &  \mkPrice{\value{Strength}} \\
    \fi

    Tinder box & 0 & \mkPrice[cp]{3} \\

    \rareMarketItem[9]{Magic beans}{0}{4}

    \ifodd\value{r2}
      Lisk-fat
    \else
      Tar
    \fi \glsfmttext{torch} & \ensuremath{\frac{1}{3}} & \mkPrice[cp]{11} \\
    Lantern oil (1~hr.) & \ensuremath{\frac{1}{3}} & \mkPrice[cp]{15} \\

  \end{nametable}
}

\newcommand\baileyTanner{
  \noindent
  \begin{minipage}{\linewidth}
  \begin{nametable}[Xcccc]{At \composeHumanName\ the Tanner's}
    \textbf{Armour} & \textbf{\Glsentrytext{dr}} & \textbf{\glsentrytext{covering}} & \textbf{Weight} & \textbf{Cost} \\\hline
    \showArmourPrice{\partialleather}{5}%
    \showArmourPrice{\completeleather}{11}%
    \showArmourPrice{\partiallisk}{31}%
  \end{nametable}
  \ifodd\value{cycle}\else
    \begin{speechtext}
      \footnotesize
      I got \mkPrice{18} if you happen to have \arabic{armourWeight} Earth \glspl{ingredient} to make some good armour.
      I can't use less, and I don't want more.
    \end{speechtext}
  \fi
  \end{minipage}
}

\newcommand\baileyRanger{
  \renewcommand\npcsymbol{\glsentrysymbol{sylf}}
  \begin{nametable}[Lcc]{Retired \Glsentrytext{ranger} \composeHumanName's Tents}
    \textbf{Size} & \textbf{Weight} & \textbf{Cost} \\\hline
    \rareMarketItem{`Stuck lock repair tools' (\absNum{r2}~Bonus) \tiny be cool or no sale, okay?}{0}{7}
    \rareMarketItem{Hardened half-yurt (\glsentrytext{dr} \arabic{r6})}{3}{12}
    \rareMarketItem[5]{Backpack (\tn[10] to remove)}{0}{2}
    \rareMarketItem{Backpack (\tn[7] to remove)}{0}{3}
    \rareMarketItem{Bagpipes}{2}{7}
    \rareMarketItem{Tent for 4}{4}{8}
    \rareMarketItem{Tent for 3}{3}{6}
    \rareMarketItem{Tent for 2}{2}{4}
    \marketItem{Tent for 1}{1}{3}
  \end{nametable}
}

\newcommand\baileySmith{
  \renewcommand\npcsymbol{\glsentrysymbol{wrecan}}
  \begin{nametable}[Lcccc]{At \composeHumanName\ the Smith's}
    \textbf{Armour} & \textbf{\Glsentrytext{dr}} & \textbf{\glsentrytext{covering}} & \textbf{Weight} & \textbf{Cost} \\\hline
    \ifnum\value{r12}>8
      \showArmourPrice{\completechain}{28}%
    \fi
    \ifnum\value{r12}>9
      \showArmourPrice{\partialplate}{38}%
    \fi
    \ifnum\thefenestraDay>50
      \ifodd\year
        \showArmourPrice{Gnome-sized \partialchain}{18}%
      \else
        \showArmourPrice{Gnoll-shaped \partialchain}{18}%
      \fi
    \fi
    \showArmourPrice{\partialchain}{18}%
  \end{nametable}
  \vspace{-\baselineskip}
  \begin{speechtext}
    \ifodd\value{r4b}
        I mostly make armour for humans, but if you need anything else, just give me a couple of days and I can make adjustments.
    \else
      What's it today?
      Some horseshoes?
      Ha!  Just kidding\ldots
      We like to have fun here.
    \fi
  \end{speechtext}
}

\newcommand\baileyFletcher{
    \renewcommand\npcsymbol{\glsentrysymbol{sylf}}
    \begin{nametable}[lYYcYc]{At \composeHumanName, the Fletcher's}

      \textbf{Projectile} & \textbf{Att} & \textbf{Dam} & \textbf{\Gls{ap}} & \textbf{Weight} & \textbf{Cost} \\\hline

      Arrows  &  --- & --- & --- & --- & \mkPrice[cp]{18}  \\

      \Glsfmttext{bow} &  +1  & +1 & 3~\glspl{ap} & 1  & \mkPrice{8}  \\

      \Glsfmttext{bow} &  +2  & +2 & 4~\glspl{ap} & 1  & \mkPrice{12}  \\

      \ifodd\value{r3}\else
      Bolt  &  --- & --- & --- & --- & \mkPrice[cp]{18}  \\
      \Glsfmttext{crossbow} &  +2  & +2 & 1~\glspl{ap} & 3  & \mkPrice{18}  \\
      \fi
    \end{nametable}
}

\newcommand\baileyArms{
  \begin{nametable}[lYcYc]{\composeHumanName's Weaponry}

  \textbf{Name} & \textbf{Attack} & \textbf{Damage} & \textbf{\Glsfmttext{weight}} & \textbf{Cost} \\\hline

    \ifodd\value{r3}\else
    Arrows  &  --- & --- &  $\frac{1}{10}$ & \mkPrice[cp]{28}  \\
    \fi

  \showWeapon{\Dagger} & \mkPrice{2} \\

  \showWeapon{\flail} & \mkPrice{2} \\

  \showWeapon{\weapon{Club}{\value{rn1t0}}{\value{rn1t2}}} & \mkPrice[cp]{3} \\

  \showWeapon{\spear} & \mkPrice{6} \\

  \ifnum\value{r3}=2%

    \showWeapon{\shortsword} & \mkPrice{9} \\

    \showWeapon{\weapon[1]{Glaive}{3}{2}} & \mkPrice{4} \\
  \else
    \showWeapon{\javelin} & \mkPrice{4} \\

    \showWeapon{\glaive} & \mkPrice{9} \\

    \showWeapon{\roundshield} & \mkPrice{3} \\
  \fi

    \showWeapon{\quarterstaff} & \mkPrice{2} \\

    \showWeapon{\weapon[1]{Longsword}{2}{2}} & \mkPrice{9} \\

  \ifodd\value{r4b}%
    \showWeapon{\buckler} & \mkPrice{3} \\
  \fi

  \end{nametable}
}

\newcommand\baileyWeaver{
  \renewcommand\npcsymbol{\glsentrysymbol{sable}}
  \begin{nametable}[Lcc]{\composeHumanName\ the weaver}

    \textbf{Clothing} & \textbf{Weight} & \textbf{Cost} \\\hline

    \Glsentrytext{dawnDolly} & 2 & \mkPrice[cp]{10} \\

    Itchy clothes & 1 & \mkPrice[cp]{30} \\

    \ifnum\value{r12}>8
      \marketItem{Orange Travelling Robes}{0}{20}
      \ifnum\value{r12}>11
        \marketItem{Red Travelling Robes}{0}{22}
      \fi
    \fi
    \ifnumcomp{\value{temperature}}{>}{0}{
      Travellers clothes & 0 & \mkPrice[cp]{60} \\
    }{
      Warm clothes & 1 & \mkPrice[cp]{95} \\
    }
    \hline

    \marketItem[cp]{Rescue kit {\footnotesize (needle, bandages, whiskey~phial: +1~Bonus)}}{0}{21}
    \marketItem{Rope, 50'}{1}{3}
  \end{nametable}
}

\newcommand\gnollSellers{
    \begin{speechtext}
    {\Large\Nl}
    Old \ifodd\value{r2}man\else woman\fi,
    your sweat stinks of scared.
    Trade for a new friend to
    \ifodd\value{r2c}
      show you courage?
    \else
      lick the fear from your face?
    \fi
    \end{speechtext}
    Six gnolls have dropped by to trade.
    Their dogs cost \mkPrice{5} worth of food, weapons, or \glspl{ingredient} (\glspl{coin} are not accepted), and the new family must show they understand how to take care of the dogs (\roll{Intelligence}{Cultivation} at \tn[8]) and provide a good name.
}

\newcommand\gnollDogShow{
  \renewcommand\animalCry{growl}
  \settoggle{allyCharacter}{true}
  \wardog[\npc{\F\A}{Dog: \weeline}]
  \animalReactions
  \columnbreak
  \wardog[\npc{\M\A}{Dog: \weeline}]
  \animalReactions
}

\newcommand\showBeastMarket{
  Cut your animal out.
  Roll for its actions each \gls{interval} it's awake.
    \settoggle{allyCharacter}{true}
    \donkey
    \animalReactions

    \horse
    \animalReactions

    \mule
    \animalReactions[\value{r6}]

    \huntingdog
    \animalReactions[3]

    \ifnum\value{r12}=7
      \cat
      \renewcommand\animalCry{mew}
      \animalReactions
    \fi
  \end{multicols}
  \begin{multicols}{2}
}

%%%%%%%%%% Town %%%%%%%%%%


\newcommand\townPitOfJustice{
  \renewcommand\npcsymbol{\glsentrysymbol{paik}}
  \begin{nametable}[Lc]{\pinLocation[-1.2,0]{Pit}\Glsentrytext{court}}
    \textbf{Service} & \textbf{Cost} \\\hline
    Front-row seat & 6~\glsfmtplural{cp} \\

    Back-row seat & 3~\glsfmtplural{cp} \\

    Rotten tomatoes & 1~\glsfmttext{cp} \\

    Snacks & 3~\glsfmtplural{cp} \\

    % Using this random counter just because nothing else is, and it won't change
    % when other numbers randomize.
    \addtocounter{spellPlusTwo}{\value{r6}}%
    `The Spectacular' & 1\arabic{spellPlusTwo}~\glspl{cp} \\

    Bribery\footnote{Bribery is paid to \pgls{sunGuard}.}
    (petty crime) & \mkPrice{30} \\

    Bribery (minor crime) & \mkPrice{60} \\

    Show of good faith (medium crime)
    \footnote{This gets you a +2 Bonus during the trial.}
    & \mkPrice{80} \\
  \end{nametable}

  \ifodd\value{r3}\relax\else
    \null
    \begin{speechtext}
      \footnotesize
      Three copper in,

      Ten gold out!
    \end{speechtext}
  \fi
}

\newcommand\townBeasts{
  \renewcommand\npcsymbol{\flourish}
  \begin{nametable}[Xc]{\marketBeastSeller's Working Beasts\pinLocation{Beasts}}

    \textbf{Beasts} & \textbf{Cost} \\\hline
    Horse & \mkPrice{20} \\

    Mule & \mkPrice{24} \\

    Hunting Dog & \mkPrice{5} \\

    Donkey & \mkPrice{2} \\

  \end{nametable}
}

\newcommand\townSquare{
  \begin{nametable}[Lc]{Central Square%
    \pinLocation[1,0]{SquareRight}%
    \pinLocation[-2,0]{Square}%
  }
    \textbf{Service} & \textbf{Cost} \\\hline
    Boat trip with \ifnum\value{r3}=3 the \composeHumanName\ sisters\else \marketBoatman\fi & \mkPrice[cp]{14}/ mile \\

    Performance by \marketBard, the Minstrel & \mkPrice[cp]{15}/ song \\

    New song composition & \mkPrice{4}/ song \\

    \ifodd\value{r4}%
      \stepcounter{r6}
      \stepcounter{footnote}
      \tiny\composeHumanName, the Fence\footnotemark[\thefootnote] & \tiny \arabic{r6}0\% and shhh\ldots \\
    \fi%

  \end{nametable}
}

\newcommand\innOne{
  \renewcommand\npcsymbol{\flourish\pinLocation{InnOne}}
  \begin{nametable}[Xc]{\pinLocation[-1.2,0]{Sidestreet}\marketInnOne}
    \textbf{Hospitality} & \textbf{Cost} \\\hline

    Hearty Meal & \mkPrice[cp]{5} \\

    \ifnum\value{temperature}>0
      Fresh \rations & \mkPrice[cp]{3} \\
    \fi

    Hardened \rations & \mkPrice[cp]{4} \\

    Rat Soup & \mkPrice[cp]{2} \\

    Basic room & \mkPrice[cp]{20} \\
  \end{nametable}
}

\newcommand\tavernOne{
  \renewcommand\npcsymbol{%
    \glsentrysymbol{abderian}%
    \pinLocation{TavernOne}%
    \pinLocation[1,1]{Crossroad}%
  }
  \begin{nametable}[Lc]{\marketTavernOne}
    \textbf{Hospitality} & \textbf{Cost} \\\hline

    \ifodd\value{r3b}\else
    Cock fight! & --- \\
    \fi

    Entrance and ale & \mkPrice[cp]{4} \\

    \ifnum\value{temperature}>0
      Sweet \rations & \mkPrice[cp]{4} \\
    \fi

    Savoury \rations & \mkPrice[cp]{5} \\

    Hearty Meal & \mkPrice[cp]{5} \\

    Rat Soup & \mkPrice[cp]{2} \\

    \ifodd\value{r4b}%
      \stepcounter{r6}
      \stepcounter{footnote}%
      \tiny\marketFence, the Fence\footnotemark[\thefootnote] & \tiny \arabic{r6}0\% and shhh\ldots \\
    \fi%
  \end{nametable}

  \ifodd\value{r4b}%
    \footnotetext{Gaining trust requires a \roll{Charisma}{Empathy} at \tn[8].}
  \fi
}

\newcommand\tavernTwo{
  \pinLocation[5.5,0]{TavernTwo}
  \renewcommand\npcsymbol{\glsentrysymbol{abderian}}
  \begin{nametable}[Lc]{\marketTavernTwo}
    \textbf{Hospitality} & \textbf{Cost} \\\hline

    Entrance and cider & \mkPrice[cp]{4} \\

    \ifnum\value{temperature}>0
      Sweet \rations & \mkPrice[cp]{4} \\
    \fi

    Savoury \rations & \mkPrice[cp]{5} \\

    Hearty Meal & \mkPrice[cp]{5} \\

    Woodspy Soup & \mkPrice[cp]{4} \\

  \end{nametable}
}

\newcommand\innTwo{
  \renewcommand\npcsymbol{\pinLocation[-1,0]{InnTwo}\glsentrysymbol{abderian}}
  \begin{nametable}[Xc]{\marketInnTwo}

    \textbf{Hospitality} & \textbf{Cost} \\\hline

    Entrance and wine & \mkPrice[cp]{14} \\

    Hearty Meal & \mkPrice[cp]{6} \\

    Nice room & \mkPrice[cp]{20} \\

    Fancy room & \mkPrice[cp]{80} \\

  \end{nametable}
}

\newcommand\townDoula{
  \noindent
  \begin{minipage}{\linewidth}
    \renewcommand\npcsymbol{\glsentrysymbol{nulla}}
    \begin{nametable}[LcX]{\pinLocation{Doula}\marketDoula's \glsentrytext{doulaShop}}
      \textbf{Things on shelves} & \textbf{Weight} & \textbf{Cost} \\\hline
      \rareMarketItem{Air \Glsentrytext{boon}}{1}{24}%
      \rareMarketItem{Fire \Glsentrytext{boon}}{1}{24}%
      \rareMarketItem{Earth \Glsentrytext{boon}}{1}{24}%
      \rareMarketItem{Water \Glsentrytext{boon}}{1}{24}%
      \rareMarketItem{Fate \Glsentrytext{boon}}{1}{24}%
      \marketItem{Cup of tea}{0}{0}%

      Blessing {\small (1D6+1 \glsfmtplural{fp})} & -- & \scriptsize`\textit{as you please}' \\
    \end{nametable}
    \vspace{-1\baselineskip}
    \begin{speechtext}
      \footnotesize
      I'll buy one Fate \glsentrytext{ingredient} for \arabic{r12}~\glsfmtplural{sp}, but no more than one.
    \end{speechtext}
  \end{minipage}
}

\newcommand\townHealers{
  \noindent
  \begin{minipage}{\linewidth}
    \renewcommand\npcsymbol{\glsentrysymbol{eldren}}
    \begin{nametable}[Lcl]{\pinLocation[-2,0]{Healers}At the \Glsentrytext{templeOfSickness}}

      \textbf{Cure} & \textbf{\Glsentrytext{weight}} & \textbf{Cost} \\\hline

      \rareMarketItem{Fate \Glsentrytext{elixir} (only \arabic{r3} left)}{1}{24}%

      \rareMarketItem[9]{Air \Glsentrytext{elixir} (only \arabic{r3} left)}{1}{24}%

      \rareMarketItem{Fire \Glsentrytext{elixir} (only \arabic{r3} left)}{1}{24}%

      \rareMarketItem[10]{Water \Glsentrytext{elixir} (only \arabic{r3} left)}{1}{24}%

      \rareMarketItem{Earth \Glsentrytext{elixir} (only \arabic{r3} left)}{1}{24}%

      \marketItem[cp]{Rescue kit {\footnotesize (needle, bandages, whiskey~phial: +1~Bonus)}}{0}{21}

      \rareMarketItem[7]{Medical box {\footnotesize (everything included: +3~Bonus)}}{2}{9}%

      \marketItem{Medical kit {\footnotesize (balms and ointments: +2~Bonus)}}{1}{3}

    \end{nametable}

    \begin{speechtext}
      \footnotesize
      \Glsfmttext{mixer} \marketMixer\ says to tell you that we'll purchase any \glsfmtplural{ingredient} for \mkPrice{12} if we're out of stock.
    \end{speechtext}
  \end{minipage}
  \null\par
}

\newcommand\townDocks{
  \stepcounter{footnote}%
  \pinLocation[9,1]{Crossroad}
  \renewcommand\npcsymbol{\flourish}
  \begin{nametable}[Lcc]{At the Docks\footnotemark[\value{footnote}]\pinLocation[-3,0]{Docks}}

    \textbf{Items} & \textbf{\Glsentrytext{weight}} & \textbf{Cost} \\\hline
    Fake \glsfmtplural{fodder} town-pass & 0 & \mkPrice{4} \\
    \rareMarketItem{Air \Glsentrytext{ingredient} (\glsentrytext{griffin} wings)}{1}{13}%
    \rareMarketItem{Fire \Glsentrytext{ingredient} (bear's heart)}{1}{13} %
    \ifnum\value{temperature}=0\rareMarketItem{Earth \Glsentrytext{ingredient} (\glsentrytext{basilisk} hide)}{1}{13}\fi %
    \rareMarketItem{Water \Glsentrytext{ingredient} (\glsentrytext{woodspy} beak)}{1}{13} %
    \rareMarketItem{Fate \Glsentrytext{ingredient} (\ifnum\value{temperature}=0 human blood from the \glsentrytext{court}\else brown ooze\fi)}{1}{14}

    Lock-pick set%
    (\absNum{rn1t2}) & 0 & \mkPrice{10} \\
  \end{nametable}
}

\newcommand\docksNote{
  \ifcase\value{r4}\relax
  \or
    \ifcase\value{cycle}
      \footnotetext{His Eternal Majesty, Sundew Eye-Eye, will give you \mkPrice{3} discount if you acknowledge him as the rightful heir to the Shattered Castle, and Rex of all \glsfmttext{fenestra}.}
    \or
      \footnotetext{By the time you arrive, the river has frozen, and everyone's too busy smashing the ice to acknowledge you.  Roll \roll{Strength}{Survival} at \tn[8] to help out over the \glsfmttext{interval}.}
    \or
      \footnotetext{\composeHumanName\ looks a bit \emph{off}.
      Roll \roll{Wits}{Medicine} at \glsfmttext{tn}~10.
      On a tie you contract `corpse hands', which slowly paralyses you (take a -1~Penalty to Dexterity every three \glsfmtplural{interval} until immobile, then the reverse).
      On a failure, you also pass the disease onto the \glsfmttext{pc} with the highest \glsfmtplural{fp}.}
    \or
      \footnotetext{You find a patch of screechmoss growing underneath the docks.  Roll \roll{Dexterity}{Survival} at \glsfmttext{tn}~10 to gain an Earth~\glsfmttext{ingredient}.}
    \else
      \footnotetext{The docks are full of stirges.  Everyone runs away or sails on immediately.  All sales are cancelled.}
    \fi
  \or
    \footnotetext{There is no sale, just $1D6$ thugs who want your money.}
  \or
    \footnotetext{\composeHumanName\ points out the obvious \gls{sunGuard} standing behind a bush, hoping to witness the illegal sale.
    You'll have to come back tonight.}
  \else
    \footnotetext{This item is illegal, and requires a \roll{Charisma}{Empathy} roll (\tn[10]), to gain trust along the line of people who lead to the real seller.
    The item requires one \glsfmttext{interval} to speak to everyone along the way.}
  \fi

}

\newcommand\townCuriosity{
  \renewcommand\npcsymbol{%
    \glsentrysymbol{yonder}%
    \pinLocation[0,0]{Library}%
  }
  \begin{nametable}[Lcc]{At the \glsentrytext{templeOfCuriosity}}

    \textbf{Item} & \textbf{Weight} & \textbf{Cost} \\\hline

    Chalk & 0 & \mkPrice[cp]{8} \\

    Copper bell & 0 & \mkPrice[cp]{30} \\

    \ifnum\value{temperature}>0
      Fresh
    \else
      Pressed
    \fi flowers & 0 & \mkPrice[cp]{2} \\

    \rareMarketItem{Lode stone}{0}{8}%

    \rareMarketItem{Magnifying globe}{2}{4}%

    \rareMarketItem{Magnifying glass}{1}{7}%

    \rareMarketItem{Strange map}{0}{5}%

    \rareMarketItem[10]{Brown gnomish hat}{0}{1}%
    \rareMarketItem[10]{Yellow gnomish hat}{0}{3}%
    \rareMarketItem[10]{Green gnomish hat}{0}{3}%
    \rareMarketItem[10]{Red gnomish hat}{0}{2}%
    \rareMarketItem[6]{Gnomish lantern {\small(needs Gnomish lantern~oil)} }{1}{9}%

    \rareMarketItem{Gnomish lantern oil (1~hr.) }{ \ensuremath{\frac{1}{10}} }{1}%

    \rareMarketItem[6]{Oil-lantern}{1}{15}%

    Lantern oil (1~hr.) & \ensuremath{\frac{1}{3}} & \mkPrice[cp]{20} \\

    Rushlights & 0 & \mkPrice[cp]{1} \\

    Soap & 0 & \mkPrice[cp]{3} \\

    Tinder box & 0 & \mkPrice[cp]{3} \\

    \ifodd\value{r2}
      Lisk-fat
    \else
      Tar
    \fi \glsfmttext{torch} & \ensuremath{\frac{1}{3}} & \mkPrice[cp]{11} \\

    Writing equipment & 1 & \mkPrice[cp]{20} \\

  \end{nametable}

  \ifodd\value{r3}
    \begin{speechtext}
      \footnotesize
      The \glsfmttext{templeOfCuriosity} can pay \mkPrice{8} for Air \glspl{ingredient}, and \mkPrice{8} for Fire.
    \end{speechtext}
  \fi
}

\newcommand\townSignage{
  \begin{minipage}{\linewidth}

  \begin{boxtable}[Ll]
    \hline
    Shop sign & \mkPrice[cp]{9} +2 per letter \\

    Send a letter  & \mkPrice[cp]{3} per mile \\

    Write a letter & \mkPrice[cp]{3} per sentence \\

  \end{boxtable}

  \begin{speechtext}
    \footnotesize
    \Glsentrytext{scrivener}~\composeHumanName\space
    \ifcase\value{r6b}\relax
    \or%
      knows nearly all of the letters!
    \or%
      likes to draw snails in the margin.
    \or%
      has five different colours of ink!
    \or%
      reminds you that `there are no spelling mistakes, just words you don't yet know'.
    \or%
      needs you to sign a contract stating that you understand that the \gls{templeOfCuriosity} will not abuse your privacy.
    \else%
      can only write \ifodd\day Dwarvish \else Gnomish \fi and Elvish.
    \fi
  \end{speechtext}
  \end{minipage}
  \null\par
}

\newcommand\townWeavers{
  \vspace{-\baselineskip}
  \begin{minipage}{\linewidth}
  \pinLocation[-0.5,-1]{Sidestreet}
  \renewcommand\npcsymbol{\glsentrysymbol{sable}}
  \begin{nametable}[Lcc]{At the \glsentrytext{templeOfFrost}\pinLocation{Weavers}}

    \textbf{Clothing} & \textbf{Weight} & \textbf{Cost} \\\hline

    \marketItem{Orange Samite Robes}{0}{15}
    \marketItem{Red Samite Robes}{0}{17}
    \marketItem{Purple Travelling Robes}{0}{23}

    \hline
    \marketItem[cp]{Sewing equipment}{0}{5}
    \marketItem{Rope, 50'}{1}{2}
    \rareMarketItem[9]{Silk rope, 50'}{0}{8}%
    \rareMarketItem[7]{Green hat}{0}{4}%
    \rareMarketItem{Orange hat}{0}{5}%
    \rareMarketItem{Purple hat}{0}{7}%
    \marketItem[cp]{Rescue kit {\footnotesize (needle, bandages, whiskey~phial: +1~Bonus)}}{0}{11}
    \ifnum\value{temperature}=0
      \marketItem[cp]{Salty \rations}{1}{5}
      \hline
      \marketItem[cp]{Warm clothes}{2}{57}
    \else
      \hline
      \marketItem[cp]{Brown cassock}{0}{57}
    \fi
    \ifnum\value{temperature}=3
      \marketItem[cp]{Wide-brimmed hat}{0}{57}
    \fi

  \end{nametable}

  \begin{speechtext}
    \footnotesize
    \ifcase\value{cycle}=0
      Got any Fate or Air \glsfmtplural{ingredient}?
      We'll pay \mkPrice{9}, happily.
    \or
      Warm those hands by the fire, deary, then tell us the news from the \glsfmttext{lonelyRoad}.
    \or
      Help yourself to some ale, but don't take the piss.
      That's the bucket on the left (we need it for the dyes).
    \or
      Welcome to the stitch `n bitch.
      What's the news from the \glsfmtplural{broch}?
    \else
      Got any Fate or Air \glsfmtplural{ingredient}?
      We'll pay \mkPrice{3}, happily.
    \fi
  \end{speechtext}
  \end{minipage}
}

\newcommand\townArmoury{
  \begin{minipage}{\linewidth}
    \renewcommand\npcsymbol{\glsentrysymbol{wrecan}}
    \begin{nametable}[Lcccc]{At the \Glsentrytext{templeOfHate}%
      \pinLocation[0.5,0]{Armoury}%
      \pinLocation[3,0]{Alley}%
    }
      \textbf{Armour} & \textbf{\Glsentrytext{dr}} & \textbf{\glsentrytext{covering}} & \textbf{Weight} & \textbf{Cost} \\\hline
      \rareArmour[5]{\completechain}{24}%
      \rareArmour[6]{\partialplate}{36}%
      \rareArmour[9]{\completeplate}{66}%
      \showArmourPrice{\partialchain}{14}%
    \end{nametable}
    \begin{speechtext}
      \footnotesize
      \ifcase\value{r3}\relax\or%
        The \glsfmttext{templeOfHate} can pay \mkPrice{8} for Earth \glspl{ingredient}.
      \or%
        Each purchase comes with a quarter bushel for your pipe.
      \else%
        We do signet rings for \mkPrice[gp]{2}.
        Custom design to suit your personality, and you can get one in silver, lead, or gnome-plated bronze.
        \Gls{coin} up-front, and ten days wait.
      \fi
    \end{speechtext}
  \end{minipage}
}

\newcommand\townTanner{
  \renewcommand\npcsymbol{\glsentrysymbol{wrecan}}
  \begin{nametable}[Lcccc]{At the Tanner's\pinLocation[-2,0]{Tanners}}
    \textbf{Armour} & \textbf{\Glsentrytext{dr}} & \textbf{\glsentrytext{covering}} & \textbf{Weight} & \textbf{Cost} \\\hline
    \rareArmour[6]{\partiallisk}{40}%
    \rareArmour[8]{\completelisk}{50}%
    \showArmourPrice{\partialleather}{5}%
    \showArmourPrice{\completeleather}{11}%
  \end{nametable}
}

\newcommand\townGuardArms{
  \renewcommand\npcsymbol{\glsentrysymbol{paik}}
  \begin{nametable}[lYYYc]{\Gls{sunGuard} Arms Sales\pinLocation[-2,0]{GuardArms}}

    \textbf{Name} & \textbf{Attack Bonus} & \textbf{Damage Bonus} & \textbf{Weight} & \textbf{Cost} \\\hline

    \showWeapon{\Dagger} & \mkPrice{4} \\

    \showWeapon{\glaive} & \mkPrice{10} \\

    \showWeapon{\greataxe} & \mkPrice{9} \\

    \showWeapon{\greatsword} & \mkPrice{15} \\

    \showWeapon{\shortsword} & \mkPrice{9} \\

    \showWeapon{\spear} & \mkPrice{7} \\

    \showWeapon{\longsword} & \mkPrice{13} \\

  \end{nametable}

  \begin{speechtext}
    \footnotesize
    \ifcase\value{r4}\relax
    \or
      I could have been \ifodd\value{r2} a carter grapher --- it's just scribble, scribble\else \pgls{armourer} --- tap-tap-tap all day\fi, easy.
      I just wanted a proper job, you know?
    \or
      Anyone speak
      \ifodd\value{r3}%
        Dwarvish%
      \else
        Gnomish%
      \fi?
      We can pay \mkPrice{2} for a translator for that shifty little shit-stain in the cells, below.
      I've been at him for hours, and I reckon he's saying that he's ready to talk.
    \or
      You look like a sly one!
      There's a reward out on `\marketFence'.
      Stolen goods.
      \mkPrice[gp]{3} reward if you can name where the git's doing business today, and wait for my boys to confirm.
    \else
      Carrying weapons in town is illegal, so buy it and fuck off!
    \fi
  \end{speechtext}
}

\newcommand\townGuardProjectiles{
  \begin{boxtable}[LYYYXl]
    \textbf{Projectile} & \textbf{Attack Bonus} & \textbf{Damage} & \textbf{\Gls{ap} Cost} & \textbf{Weight} & \textbf{Cost} \\\hline

    \Glsfmttext{bow} &  +1  & +1 & 3~\glspl{ap} & 1  & \mkPrice{9}  \\

    \Glsfmttext{bow} &  +2  & +2 & 4~\glspl{ap} & 1  & \mkPrice{11}  \\

    \ifodd\value{r4b}%
      \Glsfmttext{bow} &  +3  & +3 & 5~\glspl{ap} & 1  & \mkPrice{13}  \\
    \fi
    \ifodd\value{r3}\else
      \Glsfmttext{bow} &  +4  & +4 & 6~\glspl{ap} & 1  & \mkPrice{15}  \\
    \fi

    \hline
    Arrows  &  --- & --- & --- & --- & \mkPrice[cp]{16}  \\

    Bolt  &  --- & --- & --- & --- & \mkPrice[cp]{18}  \\
    \hline

    \Glsfmttext{crossbow} &  +2  & +2 & 1~\glspl{ap} & 3  & \mkPrice{16}  \\
  \end{boxtable}
}


