\section*{Town Market}

\hint{\showCycle}

\begin{multicols}{3}

\townPitOfJustice

\townBeasts

\townSquare

\innOne

\tavernOne

\tavernTwo

\innTwo

\randomize
\ifnum\value{r12}>7
  \townDoula
\fi

\end{multicols}

\bigLine

\begin{multicols}{2}

\townHealers

\townDocks

\townCuriosity

\townSignage

\ifcase\value{r4}\relax
\or
  \ifcase\value{cycle}
    \footnotetext{His Eternal Majesty, Sundew Eye-Eye, will give you \mkPrice{3} discount if you acknowledge him as the rightful heir to the Shattered Castle, and Rex of all \glsfmttext{fenestra}.}
  \or
    \footnotetext{By the time you arrive, the river has frozen, and everyone's too busy smashing the ice to acknowledge you.  Roll \roll{Strength}{Survival} at \tn[8] to help out over the \glsfmttext{interval}.}
  \or
    \footnotetext{\composeHumanName\ looks a bit \emph{off}.
    Roll \roll{Wits}{Medicine} at \glsfmttext{tn}~10.
    On a tie you contract `corpse hands', which slowly paralyses you (take a -1~Penalty to Dexterity every three \glsfmtplural{interval} until immobile, then the reverse).
    On a failure, you pass the disease onto the \glsfmttext{pc} with the highest \glsfmtplural{fp}.}
  \or
    \footnotetext{You find a patch of screechmoss growing underneath the docks.  Roll \roll{Dexterity}{Survival} at \glsfmttext{tn}~10 to gain an Earth~\glsfmttext{ingredient}.}
  \else
    \footnotetext{The docks are full of stirges.  Everyone runs away or sails on immediately.  All sales are cancelled.}
  \fi
\or
  \footnotetext{There is no sale, just $1D6$ thugs who want your money.}
\or
  \footnotetext{\composeHumanName\ points out the obvious \gls{sunGuard} standing behind a bush, hoping to witness the illegal sale.
  You'll have to come back tonight.}
\else
  \footnotetext{This item is illegal, and requires a \roll{Charisma}{Empathy} roll (\tn[10]), to gain trust along the line of people who lead to the real seller.
  The item requires one \glsfmttext{interval} to speak to everyone along the way.}
\fi

\townTanner

\townWeavers

\townArmoury

\end{multicols}

\bigLine
\begin{multicols}{2}

\townGuardArms

\fightAdvert

\end{multicols}

\townGuardProjectiles
