\newcommand\selectCode[1]{
  \ifcase#1%
    \def\codeName{Chronicler}%
    \def\codeValues{%
      \begin{itemize}
        \item
        Providing a recap at the start of the session.
        \item
        Uncovering a secret.
        \item
        Solving a puzzle.
        \item
        Preserving knowledge that would otherwise have been lost.
      \end{itemize}
    }%%
  \or%
    \def\codeName{Conqueror}%
    \def\codeValues{%
      \begin{itemize}
        \item
        Other players asking advice on combat tactics.
        \item
        Losing \glspl{hp}.
        \item
        Going first into a dangerous situation.
        \item
        Slaying the most powerful opponent you have slain so far, measured by \gls{cr}.
      \end{itemize}
    }%
  \or%
    \def\codeName{Jester}%
    \def\codeValues{%
      \begin{itemize}
        \item
        Executing a prank set up on a previous session.
        \item
        Making a painful pun.
        \item
        Lifting the spirits of the downtrodden.
        \item
        Finding a new type of food or drink.
      \end{itemize}
    }%
  \or%
    \def\codeName{Noble}%
    \def\codeValues{%
      \begin{itemize}
        \item
        Helping a stumped \gls{gm} come up with a quick name for a tavern, \gls{village}, or \gls{npc}.
        \item
        Being addressed deferentially.
        \item
        Disarming a potential conflict before it escalates.
        \item
        Acquiring more wealth than ever before.
      \end{itemize}
    }%
  \or%
    \def\codeName{Paladin}%
    \def\codeValues{%
      \begin{itemize}
        \item
        Declaring an action with an in-character voice.
        \item
        Punishing a law-breaker.
        \item
        Fulfilling an oath set up on a previous \gls{interval}.
        (characters can make unlimited oaths without penalty)
        \item
        Capturing a more troublesome law-breaker than ever before (measured by \gls{cr}).
      \end{itemize}
    }%
  \or%
    \def\codeName{Rebel}%
    \def\codeValues{%
      \begin{itemize}
        \item
        Tracking potential weaknesses of those in power (the player must keep a list).
        \item
        Vexing people with (some degree of) authority.
        \item
        Sabotaging the plans of those who serve the current order.
        \item
        Upturning the habits of an institution.
      \end{itemize}
    }%
  \or%
    \def\codeName{Tribalist}%
    \def\codeValues{%
      \begin{itemize}
        \item
        Bringing snacks for the table.
        \item
        Helping a member of the tribe.
        \item
        Helping \pgls{pc} gain \glspl{xp}.
        \item
        Celebrating \pgls{pc}'s birthday.
      \end{itemize}
    }%
  \else%
    \def\codeName{Wanderer}%
    \def\codeValues{%
      \begin{itemize}
        \item
        Mapping a new area (the player must draw the map).
        \item
        Remembering the name of \pgls{npc} from a previous \gls{interval}.
        \item
        Travelling somewhere new.
        \item
        Seeing a new type of creature.
      \end{itemize}
    }%
  \fi%
}
