\subsubsection*{\Glsfmtlongpl{ap}}

\begin{enumerate}

  \item
  Everyone in the room sets their \glspl{ap} to 3 + Speed.
  \item
  Every action costs at least 1 \gls{ap}.
  \item
  Circle round the table, with each player taking their turn.
  However, if any character wants to jump in, use this order:
  \begin{enumerate}
    \item
    The character who has the most \glspl{ap} goes first.
    \item
    The character doing the action which requires the least \glspl{ap} to spend.
    \item
    The character with the highest Speed.
    \item
    The character with the shortest name.
  \end{enumerate}
\end{enumerate}

\subsubsection*{Spending \Glsfmtlongpl{ap}}

Characters can spend \glspl{ap} on the following:

\begin{itemize}
  \item
  Guarding someone costs 1 \gls{ap}.
  Anyone attacking the target must successfully attack you first (without dealing Damage).
  They can then spend \glspl{ap} to attack the target immediately.
  \item
  Movement costs 1 \gls{ap} and allows people to move 3 steps + their Speed Bonus.
  \item
  Punching or pushing costs 1 \gls{ap}.
  \item
  The cost to attack depends upon the weapon.
  \item
  Taking out a weapon which has been placed to-hand costs 1 \gls{ap}.
  \item
  Using items (such as drinking potions or reading books) costs 3 \glspl{ap}.
\end{itemize}

\subsubsection*{Attacking}

The characters rolls a \textit{resisted action}.
\begin{itemize}
  \item
  Weapons require Dexterity + Combat.
  \item
  Grabbing employs Dexterity + Brawl.
  \item
  Running away uses Speed + Athletics.
\end{itemize}

\subsubsection*{Damage}

Characters have 6 \glspl{hp}, plus their Strength Bonus.

\begin{itemize}

  \item
  Fists deal 1D4 Damage.
  \item
  Weapons each have their own die-type.
  \item
  The character's Strength Bonus adds to the result.
\end{itemize}

