\spell{Choke}% Name
  {\mFate, \mAir}% Spheres
  {Wax}% Action
  {\detailed}% Enhancements
  {\roll{Strength}{Athletics}}% Resist with
  {target loses \arabic{spelllevel} \glspl{hp}}% Description
  {
    The caster insists the target has taken a wound and they begin to feel it as internal bleeding accompanies a headache.
    The target takes \dmg{spelllevel} Damage.
  }

\spell{Infectious Migraine}% Name
  {\mFate, \mAir}% Spheres
  {Wax}% Action
  {\duplicated}% Enhancements
  {\roll{Strength}{Athletics}}% Resist with
  {\spellArea\ targets lose \arabic{spelllevel} \glspl{fatigue}}% Description
  {
    As the caster roars, a deathly feeling flows over \spellArea\ targets within \spellRange\ each take \arabic{spelllevel} \glspl{fatigue}.
  }

\spell{Corpse Stench}% Name
  {\mFate, \mAir}% Spheres
  {Witness}% Action
  {\distant}% Enhancements
  {time since death}% Resist with
  {Detect any close corpses}% Description
  {
    Sniffing at the wind, the caster identifies any corpses within \spellRange.
    Casters typically use this trick to double-check if an immobile and wounded person might still have a chance of life.
  }

\spell{Preservation}% Name
  {\mFate, \mAir}% Spheres
  {Wane}% Action
  {\detailed}% Enhancements
  {target's current \glsentrytext{fatigue} penalty}% Resist with
  {Stop \glspl{fatigue}, poisons, venom or rot}% Description
  {
    The caster removes one type of death from the target -- \glspl{fatigue}, poison, venom, rot, or anything else they can think of.

    Corpses in this state no longer decay\ldots or at least delay any decay for \arabic{spelllevel} \glspl{interval}. 
    Time spent completely motionless does not count against this time, so any corpse can remain indefinitely fresh, and any poison can remain indefinitely at bay, as long as the subject does not move an inch.
  }

\spell{Soul Specks}% Name
  {\mFate, \mAir}% Spheres
  {Warp}% Action
  {\detailed}% Enhancements
  {Vigilance}% Resist with
  {Gain \gls{dr} 2, ignore up to \arabic{spelllevel}~\gls{fatigue} penalties, and see as the dead see}% Description
  {
    The caster stares into a middle distance continuously, until they find a special state of de-focussing their eyes which lets them (or a target) see as the dead see.
    They no longer see normal light, but instead see only the light of souls.
    However, the vision becomes indistinct beyond \spellRange\ -- the target understands nothing more than `something might live over there', and any life around them quickly distorts that limited vision.

    For as long as the spell remains active, the target cannot regenerate \glspl{fatigue}, \glspl{mp}, or \glspl{hp}.
  }

