\ifodd\value{diceNo}

\spell{Curse}% Name
  {}% Enhancements
  {Wane}% Action
  {Fate}% Spheres
  {\roll{Charisma}{Athletics}}% Resist with
  {The caster wishes for the target's shoes to fill up with rocks, or some other small irritation.
    The target then loses \showDam~\glspl{fp}}% Description
  {}

\spell{Fathom}% Name
  {}% Enhancements
  {Witness}% Action
  {Fate}% Spheres
  {\roll{Charisma}{Deceit}}% Resist with
  {With a short interaction, and some questions about family, the caster discerns if the target has any special fate}% Description
  {The spell produces only `yes' (if the target carries \glspl{fp}), or `no' (if they do not), without further details.}

\else

\spell{Little Blessing}% Name
  {}% Enhancements
  {Wax}% Action
  {Fate}% Spheres
  {\roll{Strength}{Brawl}}% Resist with
  {With a short pep-talk for an underdog, and a pun about size, the target gains \showDam~\glspl{fp}}% Description
  {}

\spell{Twisted Fate}% Name
  {}% Enhancements
  {Warp}% Action
  {Fate}% Spheres
  {\roll{Charisma}{Cultivation}}% Resist with
  {The \gls{witch} wishes someone a `fun day', and the next \glsfmttext{segment} occurs with next one after, meaning two \glsfmtplural{segment} at once}% Description
  {
    If someone targets \pgls{npc} with this \gls{spell}, any number of things can happen.
    \begin{dlist}
      \item
      \Pgls{monster} attacks the \gls{npc}.
      If the \gls{npc}'s \gls{cr} is less than $1D6\times2$, they meet death on the road.
      \item
      The \gls{npc} finds an urgent task.
      They disappear for a year, returning with an extravagant tale.
      \item
      The \gls{npc} becomes embroiled in the \glspl{pc}' business.
      They receive the next available \glsfmttext{segment} instead of the players.
      That \glsfmttext{segment} is missed entirely, and the \gls{gm} must approximate what occured, and allow the \glspl{pc} to hear about the results later.
      \item
      The \gls{npc} becomes enmeshed in the current \glsfmttext{thread}.
      Each subsequent \glsfmttext{segment} features this \gls{npc} in some way (though perhaps just by mention).
      \item
      The \gls{npc} gains an ally (select any other \gls{npc}).
      \item
      The \gls{npc} comes into sudden wealth, gaining $1D6 \times 2$~\glspl{gp}.
    \end{dlist}
  }

\fi
\stepcounter{diceNo}
