\ifodd\value{diceNo}

\spell{Hidden Pocket}% Name
  {Duplicated}% Enhancements
  {Warp}% Action
  {Earth, Fire}% Spheres
  {smooth terrain}% Resist with
  {The caster offers a valuable item, and a small magical gateway joins two spaces into one.
  Items with \pgls{weight} of \arabic{spellTargets} or less can fit through before it collapses}% Description
  {This little gateway opens easily when cast on openings, like an aperture or window.
  Curled bushes may provide something like an opening, but at \tn[10], while casting on a smooth surface would be \tn[14] and a gas would be \tn[16].

  These little pockets soon collapse under the weight of the wind moving through them, but any left in stagnant air can remain quietly open for decades.

  While it may seem that the spell has two targets, in fact it has one, because the two spaces become one at the point of casting.
  And while the spell is `Duplicated', this never leads to many gateway, but only a single, larger, gateway, as the spell unfolds where it begins.}

\spell{Slow Fall}% Name
  {Duplicated}% Enhancements
  {Wane}% Action
  {Earth, Fire}% Spheres
  {caster's Strength}% Resist with
  {As the caster covers their eyes, they begin to fall slower and slower.
  Any Damage from falling reduces by \arabic{spellPlusOne}}% Description
  {}

\else

\spell{Telekinetic Fist}% Name
  {Detailed}% Enhancements
  {Wax}% Action
  {Earth, Fire}% Spheres
  {weapon Damage}% Resist with
  {The caster increases any force acting on a target, increasing the Damage by \arabic{spellPlusOne}.
  This requires acting at the same \glspl{ap} level}% Description
  {For example, when someone aims a bow to strike a bandit, the caster calls to the arrow to fly fast, and it inflicts +\arabic{spellPlusOne} Damage.
  A weapon about to inflict $1D6$~Damage requires a roll at \tn[7], while \pgls{weapon} inflicting  $1D6+3$~Damage would need \tn[10], as casters need more focus to affect heavier or faster \glspl{weapon}.

    The caster cannot use this spell to attack directly, as they cannot attack at the same time as casting.}

\fi

\stepcounter{diceNo}
