\spell{Sparkle}% Name
  {\mFire, \mAir}% Spheres
  {Wax}% Action
  {}% Enhancements
  {Academics}% Skill
  {any spark blooms into a warm light}% Description
  {
    Arcanists of light can make any source of light -- even a candle flame or starlight -- bloom into the light of a healthy torch.
    When the light springs up suddenly in the dark, anyone looking towards it makes a Wits + Vigilance test (\tn{8}) or loses 1~\gls{ap}.

    The light attaches to any target -- a person or area -- then fades if left in the darkness for a full \gls{interval}.
  }

\spell{Shadow}% Name
  {\mFire, \mAir}% Spheres
  {Wane}% Action
  {}% Enhancements
  {Stealth}% Skill
  {create a patch of darkness}% Description
  {
    A single patch of darkness, the length of a step, forms anywhere within range.
    It can completely obscure a candle's light, and diminish a torch's light to the strength of a candle.

    The patch of shadow joins to a target.
    If cast on a person, the shadow remains attached to them, inflicting a -1 penalty to noticing things (and becomes very irritating, very quickly).

    The shadow fades once sunlight touches it for \pgls{interval}.
  }

\spell{Little Big}% Name
  {\mFire, \mAir}% Spheres
  {Warp}% Action
  {}% Enhancements
  {Academics}% Skill
  {single item contorts like a funhouse mirror}% Description
  {
    When light contorts, it can make something seem larger or smaller (or oscillate between the two).
    The farther something is from the target, the stranger the target appears.

    A gnome seen from ten steps might appear to be the size of a human, or a human may appear the size of a gnome.
    Of course the closer one approaches the target, the more normal it appears.

    The spell inflicts a penalty to any ranged attacks, including spells.
    Targets five steps away get a -1 penalty, those 10 steps receive a -2 penalty, and anyone further receives a -3 penalty.
  }
