\spell{Fascination}% Name
  {Fate, Water}% Spheres
  {Wax}% Action
  {}% Enhancements
  {\roll{Wits}{Academics}}% Resist with
  {target becomes enamoured with their current action, and finds it hard to stop}% Description
  {
    The target finds sudden joy and fascination with their current task.
    The task always takes the form of a single verb -- `blacksmithing', `walking', `singing' -- never something convoluted like `the mission to kidnap the warden', or `finding the right paints for the colour of a Sunrise'.

    \Glspl{npc} targeted by the spell can make a Wits + Academics roll, \tn[8], to break away from the task.
    \Glspl{pc} afflicted by the spell cannot gain any further \glspl{xp} for the a full day (four \glspl{interval}), unless they complete the current \gls{interval} without wavering from their task.

  Anyone sleeping almost certainly remains asleep, and rolls to wake up suffer a -4 penalty.
  }

\spell{Confusion}% Name
  {Fate, Water}% Spheres
  {Wane}% Action
  {}% Enhancements
  {\roll{Wits}{Academics}}% Resist with
  {the target becomes listless and distractable}% Description
  {
    The target loses their train of thought.
    They take a -1 penalty to all actions using Mental Attributes, and a -1 \gls{ap} penalty during combat.
    Anyone actively attacking the caster loses their action (but not when attacking others).
  }

\spell{Shadow Check}% Name
  {Fate, Water}% Spheres
  {Witness}% Action
  {}% Enhancements
  {}% Resist with
  {the caster checks if something has a mind}% Description
  {
    Shadows, statues, or suspicious bushes can all hide all manner of things.
    This spell tells the caster if any particular patch (and it has to be a specific patch) contains anything which has a mind.

    The spell will not say what kind of mind this is -- whether animal or person.
    It reports only `yes/ no', and often has false positives due to mice or insects (1/6 chance in daylight, 2/6 chance at night).
  }

