\ifodd\value{diceNo}

\spell{Stranger Danger}% Name
  {Distant, Duplicated}% Enhancements
  {Wane}% Action
  {Water, Fate}% Spheres
  {\roll{Wits}{Academics}}% Resist with
  {
    The caster waves to people in the distance and calls out a confusing greeting.
    It makes no sense, and confusion begins to take hold.
    The targets become disoriented, and suffer a -\arabic{spellPlusOne} penalty to all actions based on Mental Attributes}% Description
  {
    The spell lasts until the character gains \pgls{xp} for following their Code.
  }

\else

\spell{Delicate Audience}% Name
  {Detailed, Devious}% Enhancements
  {Witness}% Action
  {Water, Fate}% Spheres
  {ambient noise}% Resist with
  {With a gentle touch or wave, the caster begins to guess at the target's loudest thoughts, and receives an answer to three yes/ no questions, each more detailed than the last.
  The spell lies dormant for \pgls{interval}, then provides one more answer each interval after that}% Description
  {
  For example, the caster could ask if someone has hostile intentions, then if they have hostile intentions towards \pgls{warden}, and finally, if the hostile intentions are personal.

  The caster always has to select the next question immediately, but only the next.
  However, they must also remain close to the target for the majority of each \gls{interval}, or the spell ends.

  Many use this spell to communicate with sentient spells, such as \glspl{artefact}.}

\spell{Mind's Chatter}% Name
  {Detailed, Duplicated}% Enhancements
  {Warp}% Action
  {Water, Fate}% Spheres
  {\roll{Wits}{Academics}}% Resist with
  {With an intense stare, the caster suggests various thoughts to \arabic{spellTargets} targets.
  The targets may not believe these thoughts, but it lets the caster communicate easily}% Description
  {The targets suffer a -\arabic{spellPlusOne} Penalty to focussing on anything while the caster bestows these new thoughts.
  The spell lasts for \arabic{spellCost} \glspl{interval}.}

\fi
\stepcounter{diceNo}
